Type cones of $\b{g}$-vector fans

### 2019-02-08 thirdPaper/draft/typeConeAssociahedra.tex
Started Section 4.4.3

%%
\subsubsection{$2$-term complexes of projective modules}\label{sect::Kbproj}

>>>>

%%
\subsubsection{$2$-term complexes of projective modules}\label{sect::Kbproj}
Let~$\Lambda$ be an Artin algebra.  Then the homotopy category~$K^b(\proj \Lambda)$ is a triangulated category, and its full subcategory~$K^{[-1,0]}(\proj \Lambda)$ of complexes concentrated in degrees~$-1$ and~$0$ is closed under extensions.  Therefore, it is an extriangulated category.

We know from~\cite{} that the indecomposable objects of~$K^{[-1,0]}(\proj \Lambda)$ are in natural bijection with the indecomposable~$\Lambda$-modules and with the shifted indecomposable projective~$\Lambda$-modules.  Thus is has finitely many isomorphism classes of indecomposable objects if and only if~$\Lambda$ is representation-finite.  This gives a setting in which to apply Theorem~\ref{}.

\pg{Add introducing paragraph}

\begin{theorem}
 Let~$\Lambda$ be a brick algebra.  Then the almost-split conflations of~$K^{[-1,0]}(\proj \Lambda)$ are mutation conflations if and only if for any indecomposable~$\Lambda$-module~$M$, the space~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
\end{theorem}
\begin{proof}
 \pg{TO DO}
\end{proof}
